Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-01 Manuscript/Tabs/sim_gaus_var_slct_tab.tex
Update Variable Selection Tables (#39)

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.89 & 0.76 & 0.84 & 0.93 & 0.62 & 0.86 & 0.50 \\ 
   50 & Precision & 0.36 & 0.48 & 0.70 & 0.69 & 0.88 & 0.75 & 0.00 \\ 
  100 & Precision &  & 0.43 & 0.61 & 0.59 & 0.99 & 0.79 & 0.00 \\ 
  200 & Precision &  & 0.36 & 0.61 & 0.47 & 0.28 & 0.75 & 0.00 \\ 
    4 & Recall & 1.00 & 0.53 & 0.49 & 0.53 & 0.88 & 0.99 & 0.51 \\ 
   10 & Recall & 1.00 & 0.40 & 0.52 & 0.52 & 0.83 & 1.00 & 0.25 \\ 
   50 & Recall & 1.00 & 0.35 & 0.40 & 0.48 & 0.37 & 1.00 & 0.00 \\ 
  100 & Recall &  & 0.33 & 0.36 & 0.40 & 0.30 & 0.99 & 0.00 \\ 
  200 & Recall &  & 0.32 & 0.33 & 0.35 & 0.52 & 1.00 & 0.00 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.90 & 0.32 & 0.49 & 0.57 & 0.46 & 0.86 & 0.10 \\ 
   50 & MCC & 0.54 & 0.31 & 0.47 & 0.53 & 0.50 & 0.83 & -0.06 \\ 
  100 & MCC &  & 0.32 & 0.41 & 0.45 & 0.53 & 0.87 & -0.03 \\ 
  200 & MCC &  & 0.28 & 0.41 & 0.38 & 0.36 & 0.85 & -0.01 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.89 & 0.76 & 0.84 & 0.93 & 0.62 & 0.86 & 1.00 \\ 
   50 & Precision & 0.36 & 0.48 & 0.70 & 0.69 & 0.88 & 0.75 & 1.00 \\ 
  100 & Precision &  & 0.43 & 0.61 & 0.59 & 0.99 & 0.79 & 0.99 \\ 
  200 & Precision &  & 0.36 & 0.61 & 0.47 & 0.28 & 0.75 & 0.99 \\ 
    4 & Recall & 1.00 & 0.53 & 0.49 & 0.53 & 0.88 & 0.99 & 0.51 \\ 
   10 & Recall & 1.00 & 0.40 & 0.52 & 0.52 & 0.83 & 1.00 & 0.50 \\ 
   50 & Recall & 1.00 & 0.35 & 0.40 & 0.48 & 0.37 & 1.00 & 0.50 \\ 
  100 & Recall &  & 0.33 & 0.36 & 0.40 & 0.30 & 0.99 & 0.50 \\ 
  200 & Recall &  & 0.32 & 0.33 & 0.35 & 0.52 & 1.00 & 0.50 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.90 & 0.32 & 0.49 & 0.57 & 0.46 & 0.86 & 0.61 \\ 
   50 & MCC & 0.54 & 0.31 & 0.47 & 0.53 & 0.50 & 0.83 & 0.69 \\ 
  100 & MCC &  & 0.32 & 0.41 & 0.45 & 0.53 & 0.87 & 0.70 \\ 
  200 & MCC &  & 0.28 & 0.41 & 0.38 & 0.36 & 0.85 & 0.70 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}
